HERA Dish Reflectometry

### 2015-11-04 DishReflectometry/Memo.tex

\documentclass[12pt,preprint]{aastex}
\usepackage{float,amsmath}
%\usepackage[margin=1in]{geometry}
%\usepackage{titlesec} %used to format titles
\usepackage{graphicx} %for handling figures
%\usepackage[none]{hyphenat} %disallows hyphenated words
\newcommand{\vdag}{(v)^\dagger}
\newcommand{\volt}{{v}}
\newcommand{\vis}{{V}}
\newcommand{\sky}{{\rm sky}}
\newcommand{\bmvolt}{{a}}
\newcommand{\bm}{{A}}
\newcommand{\thhat}{{\hat\theta}}
\newcommand{\fngexp}{{e^{\frac{2\pi i\nu\vec{b}\cdot\thhat}{c}}}}
\newcommand{\ifngexp}{{e^{-\frac{2\pi i\nu\vec{b}\cdot\thhat}{c}}}}
\newcommand{\myemail}{skywalker@galaxy.far.far.away}

%\usepackage{cite}

%\citestyle{aa}
\shorttitle{HERA dish reflectometry }
\shortauthors{Patra et al.}

@@

\title{Effect of multiple reflection of the sky signal off the HERA element on the measurements of 21cm power spectrum} 
%\maketitle

\author{Nipanjana Patra\altaffilmark{1} }
\email{Contact author email: nipanjana@berkeley.edu}

\author{Zaki Ali\altaffilmark{1}, Carina Cheng\altaffilmark{1}, Dave DeBoer\altaffilmark{1}}
\author{Gilbert Hsyu\altaffilmark{2}, Tsz Kuk Leung\altaffilmark{2}, Aaron Parsons\altaffilmark{1}}
% XXX add all members of HERA collaboration
% XXX suggest Patra, Parsons, Ali, DeBoer, Cheng, Leung, Hsyu, alphabetical

\altaffiltext{1}{University of California, Berkeley, nipanjana@berkeley.edu}
\altaffiltext{2}{To be inserted}

\begin{abstract}
\end{abstract}

@@

Since it was first proposed in \citet{shaver_et_al1999}, measuring 21~cm
emission from neutral hydrogen in our early universe has gained attention as a
powerful probe of both cosmology and astrophysics.  While the science case for
21~cm cosmology, particularly during the Epoch of Reionization, is well
established (see, e.g.,
\citealt{furlanetto_et_al2006,morales_wyithe2010,furlanetto_loeb2014,pritchard_loeb2014}),
the technical path toward measuring this signal has been more problematic.  The
weakness of this hyperfine line keeps the 21~cm signal below opacity throughout
cosmological history, but it also creates sensitivity and calibration
challenges that have yet to be fully solved.  With noise temperatures dominated
by sky noise \citep{XXX} and foregrounds four to five orders of magnitude
brighter than the signal \citep{XXX}, 21~cm reionization experiments must
furnish both collecting area and foreground suppression at levels significantly
beyond anything previously achieved in radio telescopes operating below 1 GHz.

One of the most problematic effects facing these experiments results form instrument
chromaticity.  The spectral dimension of 21~cm reionization experiments is of vital
importance; for line emission, this coordinate translates to a line-of-sight distance
that can be used to construct three-dimensional maps (and power spectra) of emission,
as well as probe the evolution of 21~cm emission over cosmological timescales.
The evolving response of a radio telescope --- either a single dish
or an interferometer --- versus spectral frequency modulates spectrally smooth foregrounds ,
contaminating spectral modes that might
otherwise be used to measure reionization \citep{XXX}.  Moreover, the chromaticity of
a telescope's response pattern scales linearly with diameter, putting the
needs of foreground suppression and signal sensitivity in direct tension with one
another.

% XXX the wedge

The efficacy of the techniques of foreground removal from the measured data critically limits the 21~cm power spectrum measurements. The delay transformation technique of foreground removal, introduced by  \citep{ParsonsBacker2009,Parsons2012} computes the Fourier transform of the visibility measured by an interferometer and produces a spectrum, referred to as delay spectrum hereafter, which is a function of the geometric time delay corresponding to the physical length of the baseline between two antennas. For the visibilities measured over a wide field across wide frequency bandwidth, the delay spectrum is constituted by the instrument response, the foreground signal and 21cm power spectrum, hereafter referred to as EoR signal.
%The complex visibility measured by an interferometer is a convolution of the instrument response with the true sky response in the UV plane. Therefore, when Fourier transformed, the delay spectrum is the multiplication of the sky response with the instrument response in the delay domain.
The technique exploits the smooth spectral characteristics of the foreground and for a widefield wide bandwidth visibility measurement by an interferometer with a baseline $b$, confines the foreground contribution to the computed delay spectrum within the largest possible time delay $\tau = b/c$ corresponding to the given baseline length. Such techniques also assumes a spectrally smooth instrumental response whose contribution to the measured data, much as the contribution of the smooth spectrum foreground, also has an upper bound in the delay space imposed by the largest geometric delay of the given baseline. 
Beyond this limit, for an ideal system performance, the delay spectrum would be dominated by any wideband signal across the sky with spectral and spatial fluctuation over small scale such as the EoR signal and therefore, could be detectable.\\ 
The interaction between the sky signal and instrument response can alter the relative contribution of the foreground, instrument response and the EoR signal at a given delay and thus influence the detectability of the EoR signal. Such interactions may cause the foreground and systematics to spill over at higher delays and thus push the upper limit of the foreground and systematic contaminated delay modes to much higher delays. In this process, the EoR signal over large spatial scale will be lost.

 The Hydrogen Epoch of Reionization Array (HERA) is a proposed array consisting of 568 14-m dishes in South Africa which will measure the 21~cm power spectrum between 100 to 200~MHz . In this paper, we investigate the performance of the individual HERA elements and resulting contribution of the instrument response to the delay spectrum. Reflectometry measurements  are carried out across wide bandwidth on a prototype HERA element in Green
Bank, WV (Figure \ref{fig:heradish}) and the results are interpreted in the light of delay spectrum technique. Section 2 describes the delay spectrum for the ideal and non-ideal performance of a two element interferometer. Reflectometry measurements are described in section 3. Section 4 qualifies the performance of the HERA element as an interferometer for detection of the 21~cm power spectrum.

@@

\section{Visibility measurements by a two element interferometer}

Consider a two element interferometer with a baseline $\vec b$ and antenna field pattern $A(\thhat, \nu)$. If we denote the electric field sky signal in direction $\thhat$ by $\volt_\sky(\vec \theta, \nu)$ and the receiver noise of each element as $\volt_{rec}(\nu)$ then the voltage output of each antenna may be written as,  
\begin{equation}
\volt_{1}(\thhat, \nu) = \bmvolt_{1}(\thhat,\nu)\volt_\sky(\thhat,\nu)\nonumber\\
\end{equation}
\begin{equation}
\volt_{2} (\thhat, \nu)= \bmvolt_{2}(\thhat,\nu)\volt_\sky(\thhat,\nu)\fngexp\nonumber\\
\end{equation}
where $\bmvolt_{1}(\thhat,\nu)$ and $\bmvolt_{2}(\thhat,\nu)$ are the electric field response patterns 
of the two antennas.
Hence, the time averaged visibility measured by the interferometer may be written as, 
\begin{equation}
\vis(\vec b, \nu) =  \int  \volt_{1}(\thhat,\nu)  \volt_{2}^{*} (\thhat, \nu) \ifngexp d\Omega 
\label{eq1}
\end{equation}

We define antenna cross power pattern as  $\bm(\thhat,\nu)=\bmvolt_{1}(\thhat,\nu)\bmvolt_{2}^{*}(\thhat,\nu)$ and denote the sky intensity as  $I_\sky(\thhat,\nu)=\volt_\sky(\thhat,\nu)\volt_\sky^{*}(\thhat,\nu)$. Hence, 
\begin{equation}
\vis(\vec b,\nu) = \int \bm(\thhat, \nu) I_\sky(\thhat,\nu) \ifngexp d\Omega
	%	& = & \int B(l,m, \nu) I_{sky}(l,m,\nu) exp(-2\pi i \nu \tau_{g} ) dl dm \nonumber\\
 	%	& = & B(\vec u,\nu) \ast P_{sky}(\vec u,\nu ) \nonumber\\
	%	& = & B(\nu { |\vec b| \over c} , \nu) \ast P_{sky}(\nu { |\vec b| \over c} , \nu) \nonumber\\
	%	& = & B(\tau_{g}, \nu) \ast P_{sky}(\tau_{g} , \nu)	
\label{eq2}
\end{equation}

%i.e, the complex visibility is the Fourier transform of the product of the antenna beam pattern with the sky angular power spectrum. In other words, it is the convolution of the Fourier transform of the antenna power pattern with the Fourier transform of the sky. The complex visibility measured by an interferometer with a given baseline length has explicit dependence on frequency as well as implicit frequency dependence through the spatial frequency $\vec u = \nu { \vec b \over c}$ component. Since $\vec u $ is the For a given baseline length $|\vec b|$, the visibility measured at various frequencies are not only the function of frequencies but also samples different $\vec u$ in the uv space. Delay transformation technique takes the visibility measurements at different frequencies and Fourier transforms the complex visibilities. If we defineI_{sky} the Fourier conjugate of the frequency axis as $\tau$ then the equation could be written as, 
In \citet{parsons_et_al2012a}, the Fourier transform of the visibility along the frequency axis was introduced,
resulting in the delay spctrum:
\begin{equation}
\tilde V(\vec b, \tau)  = \int\!\!\int{\bm(\thhat,\nu) I_\sky(\thhat,\nu) \ifngexp d\Omega~e^{-2\pi i\nu\tau} d\nu}
						%   & = & \int \left [B(\tau)\ast I_{sky}(\tau) \ast \delta(\tau+\tau_{g}) \right ] dl dm	
\label{eq3}
\end{equation}

Hence, the delay spectrum, integrated over all sky would be written as, 
\begin{eqnarray}
\mathcal{F} \left [V e^{i\phi}\right]   & = &  \left [B(\tau)\ast I_{sky}(\tau) \ast \delta(\tau+\tau_{g}) \right ] 	
\label{eq4}
\end{eqnarray}
% XXX rethink how to express this equation (not correct about integrated over all sky)
% XXX define tau_g
the convolution being carried out along the $\tau$ axis which is Fourier conjugate of the frequency $\nu$. In words, the sky delay spectrum is convoluted with the delay spectrum of the instrument and is centred at a delay $\tau_{g}$. The projected geometric delay $\tau_{g}$ for a given baseline can vary from 0 to $\tau_{g}$. Also, due to frequency dependence of the sky signal, the delay spectrum of the sky spills over the delay $\tau> \tau_{g}$ with decaying amplitude [Ref to the figure Parsons12]. Sky delay spectrum $I_{sky}(\tau)$ is contributed by the foreground  $I_{fg}(\tau)$ and the 21~cm power spectrum $I_{21}(\tau)$. Since $I_{fg}$ is spectrally smooth, whereas $I_{21}$ contains spectral structures, for wideband measurements, the relative strength of the smooth spectrum foreground with respect to the delay spectrum of the $I_{21}$ reduces at higher delays and, therefore, at higher delays, the 21~cm delay spectrum is detectable.  \textbf{[ Reference to Nithya's foreground simulation work, reference to any plots on the relative contribution of the  foreground and EoR signal. ]}

\section{Effects of additional reflections of the sky signal between the parabolic dish and the feed on the measured visibility}
 Plane waves incident on a parabolic dish are focussed at the feed which is kept at the focal plane of the dish. The mismatch between the impedance of free space and the feed and transmission line results in a partial coupling of the sky signal into the feed while the rest is reflected off the feed. The reflected signal illuminates the dish and most of it is reflected back into the space. However, a part of it reflects back and forth several times in between the feed and the vertex of the dish which is shadowed by the feed (dashed blue arrows in Figure \ref{fig:cartoon}). Such reflections generate multiple copies of the incident sky signal of reduced strength at various time/phase and thus produces spurious correlations in the visibilities of interferometric data. In this section we compute the visibility of a two element interferometer accounting for the additional reflections of the sky signal in between the feed and the dish vertex and the corresponding effects on the delay spectrum.

\begin{figure}[ht!]
\centering
\includegraphics[totalheight=0.35\textheight]{plots/reflection_cartoon.png}
\caption{The blue solid lines represent an original sky signal entering the
feed. A small percentage of it (dashed blue) is reflected off the dish, and it
is these reflections that we are concerned about. In our measurements however,
the reflections measured contain most of the original pulse signal (solid red),
so it is crucial to adjust for this difference in our analysis.}
\label{fig:cartoon}
\end{figure}

Consider again a two element interferometer as described in section 2. Two antennas are assumed to be exactly identical so that their electrical parameters are same. We denote the voltage reflection coefficient of each feed by $\Gamma_{f}$. The voltage reflection coefficient of the reflector dish is denoted by $\Gamma_{d}$. Upon first incidence of the sky signal onto the dish, the entire sky signal would be reflected and focussed onto the feed. Hence, for first incidence $\Gamma_{d}=1$. Sky signal that would return to the dish after successive reflections off the feed and the dish is only reflected from a small area around the vertex of the dish and therefore, $\Gamma_{d}<1$. In our analysis, we consider one reflection of the sky power from the feed and subsequent reflection off the dish as one single reflection. If the focal length of the dish is $l$, assuming the feed is located at the focus, the roundtrip delay after first reflection will be $\Delta \tau = {2l \over c}$.

\subsection{Effect of first order reflections on visibility and delay spectrum}
Upon first incidence of the sky signal $V_{sky}$, $\Gamma_{f}$ fraction of the voltage is reflected off the feed while $(1-\Gamma_{f})$ fraction is coupled to the feed. The reflected voltage then further reflected off the dish and $(1-\Gamma_{f}) $ fraction of it reenters the feed with a roundtrip time delay $\Delta \tau$. Hence, the net voltage at the output of the two antennas could be written as,    
\begin{eqnarray}
V_{1} & = & A V_{sky}(1-\Gamma_{f}) + A V_{sky} \Gamma_{f} \Gamma_{d} e^{2\pi i\nu \Delta \tau}  (1-\Gamma_{f})^{2}\nonumber\\
         & = & A V_{sky} (1-\Gamma_{f}) \left [ 1+ (1-\Gamma_{a})\Gamma_{f} \Gamma_{d} e^{2\pi i\nu \Delta \tau} \right]\nonumber\\
\label{eq4}
\end{eqnarray}
\begin{eqnarray}
V_{2} & = & A V_{sky}(1-\Gamma_{f}) + A V_{sky} \Gamma_{f} \Gamma_{d} e^{2\pi i\nu \Delta \tau} (1-\Gamma_{f})^{2}exp({2\pi i \nu \vec{b}.\hat{s} \over c} )\nonumber\\
         & = & A V_{sky} (1-\Gamma_{f}) \left [ 1+(1-\Gamma_{a}) \Gamma_{f} \Gamma_{d} e^{2\pi i\nu \Delta \tau}  \right]exp({2\pi i \nu \vec{b}.\hat{s} \over c} )\nonumber\\
\label{eq5}
\end{eqnarray}
Frequency as well as angular dependence of the quantities are not written explicitly for notational simplicity. 
The two antennas are assumed to have identical beam pattern which is $A_{1}=A_{2} =A$. We also absorb the common gain term $(1-\Gamma_{f})$ with antenna response $A$ and denote them as $A_{f}= A(1-\Gamma_{f})$ here after. Hence, the complex visibility could be,

\begin{eqnarray}
V e^{i\phi}(\nu) & = & \int V_{1}V_{2}^{*} d\Omega \nonumber\\
		        & = & \int |A_{f}|^{2}|V_{sky}|^{2} |\left [ 1+(1-\Gamma_{f}) \Gamma_{f} \Gamma_{d} e^{2\pi i\nu \Delta \tau}  \right]|^{2} exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega
\label{eq6}		        
\end{eqnarray}

 Furthermore, combining all the terms that contain instrument response we define a common instrument parameter, written as, 
\begin{eqnarray}
\Sigma(\vec \theta, \nu) & = & |A_{f}|^{2} |\left [ 1+ (1-\Gamma_{f}) \Gamma_{f} \Gamma_{d} e^{2\pi i\nu \Delta \tau} \right]|^{2}\nonumber\\
 	    & = &  |A_{f}|^{2}  \left[ 1+ |(1-\Gamma_{f})|^{2}|\Gamma_{f}|^{2}|\Gamma_{d}|^{2} + 2 \Re \left ( (1-\Gamma_{f})\Gamma_{f}\Gamma_{d} e^{2\pi i\nu \Delta \tau} \right) \right] 
\label{eq{7}}	    
\end{eqnarray}

Instrumental response function acquires additional terms arising due to correlation between the directed and reflected component of the sky signal. The total visibility at any frequency would be the sum of the three visibilities contributed by three sources of correlated power. First term in the square bracket represents the cross correlation between the two antenna outputs contributed by the sky signal upon first direct incidence. The second term results from the cross correlation between two reflected signals in each antenna.The last term represents the cross correlation between the first direct incident signal of one antenna and the first reflected signal from the other antenna and vice versa.

Fourier transform of this visibility spectrum along the frequency axis results in the delay spectrum. 
 Fourier transform of the visibility contributed by any two voltage components from two antennas with no mutual delay is centred at a delay $\tau = \tau_{g}$ in the delay spectrum whereas any two voltage components from two antennas components having a mutual delay of $\Delta \tau$ will be centred at $\tau_{g} +\Delta \tau$. Therefore, the correlation between the reflected signal  from the feed and subsequently from the dish with the direct signal thus extends the foreground response to delays beyond the maximum geometric delay for a given baseline and contaminates the delay mode where 21~cm delay spectrum could potentially be detected. Also, any reflections arriving at the feed at any non-zero  value of the delay $\Delta \tau$ which could be the result of reflections from the feed structures would also generate non zero delay response at those delays. 
If the dish vertex is so constructed such that the reflection from the dish vertex is negligible i.e, $\Gamma_{d}<<1\ or = 0$ then the second and the third term of the $\Sigma$ vanish. Also, if we assume a $\Gamma_{a} =-10dB$ and $\Gamma_{d}= -20dB$, the second term in the expression of $\Sigma(\vec \theta, \nu)$ becomes negligible compared to the first and the third term of the expression and, therefore, can be neglected. \\

\subsection{Effect of higher order reflection on the delay spectrum} 
Correlation between the higher order reflections of the signal in any antenna with the direct component of the other would result in a delay response at integral multiple of $\Delta \tau$ and vice versa. 
If $I_{sky}$ is reflected n times in between the feed and the dish, the net voltage entering the feed after an
$n^{th}$ reflection off the feed and the dish is written as:
\begin{equation}
V_{1} =  A V_{sky}(1-\Gamma_{f})[1+ \Gamma_{f}\Gamma_{d} e^{i\phi}+ (\Gamma_{f}\Gamma_{d})^2e^{i2\phi}+ ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{in\phi}]
\end{equation}
and,

\begin{equation}
V_{2} = A V_{sky}(1-\Gamma_{f})[1+ \Gamma_{f}\Gamma_{d} e^{i\phi}+ (\Gamma_{f}\Gamma_{d})^2e^{i2\phi}+ ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{in\phi}]
\end{equation}

where $\Phi = 2\pi\nu\Delta \tau$. The relevant terms in the corresponding visibility and subsequently in the delay spectrum would be the ones which represent the correlation between the direct component of one antenna with the reflected components of the other resulting in higher order terms  in $\Sigma(\vec \theta, \nu)$. The corresponding instrument response may be written as,

\begin{equation}
\Sigma(\vec \theta, \nu) = A_{f} \left [ 1+ 2 \Re \left [(1-\Gamma_{f})( \Gamma_{f}\Gamma_{d} e^{i\phi}+ (\Gamma_{f}\Gamma_{d})^2e^{i2\phi}+ ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{in\phi}) \right ]\right ]
\end{equation}

and the measured visibility spectrum, integrated over all sky would be, 
\begin{equation}\label{eqn:series1}
V_{meas}  = I_{sky}A_{f}\Sigma( \nu)
\end{equation}

The design specification of HERA elements requires that any
signal, arriving at the feed at a delay $\Delta \tau$ with respect to the direct incidence, should be
at the level of $-60dB$ at a delay of $60ns$ relative to the first incident
signal at the feed \citep{parsons_deboer_memo}. This specification was
approximated based on the power level of the cosmological signal in relation to
foreground signals, which is estimated to be six orders of magnitude fainter
\citep{santos_et_al2005,ali_et_al2008,deoliveira2008,jelic_et_al2008,bernardi_et_al2009,bernardi_et_al2010,ghosh_et_al2011}. Additionally, the $14m$ HERA baselines set a foreground containing
horizon-limit (the wedge) that, with some buffer, sets a delay specification of
$60ns$
\citep{parsons_et_al2012b,vedantham_et_al2012,nithya_et_al2013,liu_et_al2014a,liu_et_al2014b}. Our goal is to determine the effect of the instrument response $\Sigma(\nu)$ on the delay spectrum measurement. 
\section{Measurements}
We carried out reflectometry measurements at the HERA element prototype in Green
Bank, WV (Figure \ref{fig:heradish}) in order to measure the instrument response of the feed and dish assembly and characterise its performance. As HERA progresses as
an experiment, it is necessary to build optimised dishes that aim to minimise the
challenges of chromaticity in our quest for the Epoch of Reionization.

As given in the previous section, if the incident power from the sky signal is $I_{sky}$, the feed
reflection coefficient is $\Gamma_{f}$, and the dish reflection
coefficient is $\Gamma_{d}$, then the net power entering the feed after
$n^{th}$ reflection off the feed and the dish (i.e, the sky integrated visibility spectrum) is:

\begin{equation}\label{eqn:series1}
I_{meas} =  I_{sky}A_{f}[1+ \Gamma_{f}\Gamma_{d} e^{i\phi}+ (\Gamma_{f}\Gamma_{d})^2e^{i2\phi}+ ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{in\phi}]
\end{equation}

where, $\phi = 2\pi i\nu \Delta \tau$ is the roundtrip propagation delay of a lightwave of frequency $\nu$ due to a reflection over the focal distance $l$. It is noted that upon the first incidence, the sky signal is focussed onto the feed from the entire dish and the dish reflection coefficient $\Gamma_{d}$ is $1$ for this first incidence. The subsequent back and forth reflection of the signal in between the feed and the dish, however, occurs from only the part of the dish which is shadowed by the feed. Therefore, in this case, $\Gamma_{d} < 1$.

Simplifying Equation \ref{eqn:series1}:
\begin{eqnarray}\label{eqn:ratio1}
{I_{in} \over I_{sky} } & = & A_{f}[1+ \Gamma_{f}\Gamma_{d} e^{i\phi}+ (\Gamma_{f}\Gamma_{d})^2e^{i2\phi}+ ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{in\phi}] \nonumber\\
      & = & A_{f} \displaystyle\sum\limits_{n=0}^{n} [\Gamma_{f}\Gamma_{d}e^{i \phi}]^{n}\nonumber\\
      & = & A_{f}+A_{f} \displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}e^{i \phi}]^{n}
\end{eqnarray}

In our experimental set-up, we use the feed as a transmitter and transmit a pulse. If the initial pulse is a broadband signal,
$I_{tr}$, sent to the feed via a $75ft$ cable by a vector network
analyser (VNA), a delay domain measurement of the system is accomplished by
taking the Fourier transform of the complex return loss of the feed measured by VNA. When the signal is incident on
the feed, part of the incident power ($\Gamma_{f}$) is reflected back to the
measuring device (dashed red arrows in Figure \ref{fig:cartoon}) and
$(1-\Gamma_{f})$ is radiated by the feed (solid red arrows in Figure
\ref{fig:cartoon}) which illuminates the dish. While most of the incident signal is reflected back into space by the dish, the reflected signal from the dish vertex returns to
the feed. This incident signal is now
reflected back and forth in between the feed and the dish much like the sky
signal reflection discussed previously.  Hence, if $I_{r}$ is the power
incident back on the feed for the first time then the reflected power, $I_{refl}$,
back into the VNA would be:

\begin{equation}\label{eqn:series2}
I_{refl} =  I_{r}A_{f}[1+ \Gamma_{f}\Gamma_{d} e^{i\phi}+ (\Gamma_{f}\Gamma_{d})^2e^{i2\phi}+ ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{in\phi}]
\end{equation}

@@

Recall that $I_{r}$ is the initial power that is incident back on the feed, which is just the feed radiated power reflected off the dish:

\begin{equation}
I_{r}= \Gamma_{d}(1-\Gamma_f)e^{i\phi} I_{tr}
\end{equation}

@@

\begin{eqnarray}
I_{ret} & = & \Gamma_{f}I_{tr} \nonumber\\ 
 & + &   \Gamma_{d}(1-\Gamma_f)e^{i\phi} I_{tr}(1-\Gamma_{f}) [1+ \Gamma_{f}\Gamma_{d} e^{i\phi}+  ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{in\phi}]\nonumber\\
 \end{eqnarray}

@@

  \begin{eqnarray}\label{eqn:ratio2}
 {I_{ret} \over I_{tr} } & = & \Gamma_{f}
  +  \Gamma_{d}(1-\Gamma_f)^{2} [e^{i\phi}+ \Gamma_{f}\Gamma_{d} e^{i2\phi}+  ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{i n\phi}]\nonumber\\
  & = & \Gamma_{f} + { (1-\Gamma_f)^{2}\over \Gamma_{f} } \displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}e^{i\phi}]^{n}
   \nonumber\\
\end{eqnarray}

@@

The VNA measures the magnitude and phase of the quantity ${I_{ret}\over I_{tr}}$
as a function of frequency as shown in Figure \ref{fig:freq}. In our measurement
set-up, the first reflection occurs at the feed $\Gamma_{f}$, so
$({I_{ret} \over I_{tr} }  - \Gamma_{f}) $ gives an estimate of the delay
spectrum of the sky signal. In delay domain, the relative signal strength at
zero delay represents the factor $\Gamma_{f}$ while the signal strength at any
other delay represents any delayed signal that enters the feed after being
reflected from the feed surroundings.

>>>>

\documentclass[12pt,preprint]{aastex}
\usepackage[margin=1in]{geometry}
\usepackage{float,amsmath}
%\usepackage{titlesec} %used to format titles
\usepackage{graphicx} %for handling figures
%\usepackage[none]{hyphenat} %disallows hyphenated words
\citestyle{aa}

@@

\title{HERA Dish Reflectometry} 
\author{Nipanjana Patra, Zaki Ali, Carina Cheng, Dave DeBoer, Gilbert Hsyu, Tsz Kuk Leung, Aaron Parsons}
\maketitle

@@

There are several different sources of instrumental chromaticity for radio
telescope systems that can result in non-ideal performances and unwanted
systematic effects in measured data. One such source is the mismatch between
the impedance of free space and the feed and transmission line, which results
in a partial coupling of the sky signal into the feed while the rest is
reflected back into the space. For any reflector telescope, such as HERA, this
signal illuminates the dish and part of it reflects back and forth several
times in between the dish feed and the vertex of the dish.  Such reflections
generate multiple reduced strength copies of the incident sky signal at various
delays, and this produces spurious correlations in the visibilities of
interferometric data.

To first order, the design specification of HERA elements requires that any
delayed signal, arriving at the feed after a multipath propagation, should be
at the level of $-60dB$ at a delay of $60ns$ relative to the first incident
signal at the feed \citep{parsons_deboer_memo}. This specification was
approximated based on the power level of the cosmological signal in relation to
foreground signals, which is estimated to be six orders of magnitude fainter
\citep{santos_et_al2005,ali_et_al2008,deoliveira2008,jelic_et_al2008,bernardi_et_al2009,bernardi_et_al2010,ghosh_et_al2011}.
Additionally, the $14m$ HERA baselines set a foreground containing
horizon-limit (the wedge) that, with some buffer, sets a delay specification of
$60ns$
\citep{parsons_et_al2012b,vedantham_et_al2012,nithya_et_al2013,liu_et_al2014a,liu_et_al2014b}.

We carry out reflectometry measurements at the HERA element prototype in Green
Bank, WV (Figure \ref{fig:heradish}) in order to understand the nature of feed
reflections in the dish and characterize its performance. As HERA progresses as
an experiment, it is necessary to build optimized dishes that aim to minimize the
challenges of chromaticity in our quest for the Epoch of Reionization.

@@

\section{Theory}{\label{sec:theory}}
\begin{figure}[ht!]
\centering
\includegraphics[totalheight=0.35\textheight]{plots/reflection_cartoon.png}
\caption{The blue solid lines represent an original sky signal entering the
feed. A small percentage of it (dashed blue) is reflected off the dish, and it
is these reflections that we are concerned about. In our measurements however,
the reflections measured contain most of the original pulse signal (solid red),
so it is crucial to adjust for this difference in our analysis.}
\label{fig:cartoon}
\end{figure}

Plane waves incident on a parabolic dish
are focussed at the feed with focal height $l$. For a well-designed feed, one
that closely matches the impedance of free space\footnote{The impedance of free space
is $Z_{0} = \mu_{0}c_{0} = \frac{1}{\epsilon_{0}c_{0}} \approx 377\Omega $.},
most of the signal will enter the system while only
a small percentage will be reflected back towards the dish for a secondary
reflection into the feed (dashed blue arrows in Figure \ref{fig:cartoon}). In the
following discussion, we consider a reflection off the feed and the
subsequent reflection off the dish as one reflection.

Quantitatively, if the incident power from the sky signal is $P_{sky}$, the feed
reflection coefficient is $\Gamma_{f}$, and the dish reflection
coefficient is $\Gamma_{d}$, then the net power entering the feed after an
$n^{th}$ reflection off the feed and the dish is:

\begin{equation}\label{eqn:series1}
P_{in} =  P_{sky}(1-\Gamma_{f})[1+ \Gamma_{f}\Gamma_{d} e^{i\phi}+ (\Gamma_{f}\Gamma_{d})^2e^{i2\phi}+ ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{in\phi}]
\end{equation}

where, $\phi = 2l({2\pi \over c})\nu$ is the propagation delay of a lightwave of frequency $\nu$ due to a reflection over a focal distance $l$. It is noted that upon the first incidence, the sky signal is focussed onto the feed from the entire dish and the dish reflection coefficient $\Gamma_{d}$ is $1$ for this first incidence. The subsequent back and forth reflection of the signal in between the feed and the dish, however, occurs from only the part of the dish which is shadowed by the feed. Therefore, in this case, $\Gamma_{d} < 1$.

Simplifying Equation \ref{eqn:series1}:
\begin{eqnarray}\label{eqn:ratio1}
{P_{in} \over P_{sky} } & = & (1-\Gamma_{f})[1+ \Gamma_{f}\Gamma_{d} e^{i\phi}+ (\Gamma_{f}\Gamma_{d})^2e^{i2\phi}+ ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{in\phi}] \nonumber\\
      & = & (1-\Gamma_{f}) \displaystyle\sum\limits_{n=0}^{n} [\Gamma_{f}\Gamma_{d}e^{i \phi}]^{n}\nonumber\\
      & = & (1-\Gamma_{f})+(1-\Gamma_{f}) \displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}e^{i \phi}]^{n}
\end{eqnarray}

The ratio in Equation \ref{eqn:ratio1} quantifies the amount of power received
with respect to the incident sky power. Realistically, the incident sky power
is not easily quantifiable, but it is a quantity we need to know to accurately
characterize reflections.  
%The right hand side of this equation consists of system parameters which are all chromatic i.e, functions of frequency.

%Reflections cause the sky signal to appear at various delays. We aim to measure
%the relative signal strength at those various delays, referred to as the
%``delay spectrum" hereafter, to estimate levels of reflections in between the
%feed and the dish apex.

%We employ the reciprocity theorem for antennas in our experimental set-up.
%More specifically, our experimental set-up differs from measuring sky signal
%reflections since we send a pulse that is to be transmitted from the feed
%before receiving it again. This results in a reversed situation - most of our
%original signal is transmitted from the feed to be reflected from the dish,
%while a small percentage reflects back down the cable (red arrows in Figure
%\ref{fig:cartoon}). Therefore, since our measurement is carried out in
%transmitting mode while an observation would be carried out in receiving mode,
%we correct our results in order to map them to represent real observations.

In our experimental set-up, instead of using sky signal, we employ
our feed as a transmitter and transmit a pulse. If the initial pulse is a broadband signal,
$P_{tr}$, sent to the feed via a $75ft$ cable by a vector network
analyser (VNA), a delay domain measurement of the system is accomplished by
taking the Fourier transform of the measured complex return loss of the feed. When the signal is incident on
the feed, part of the incident power ($\Gamma_{f}$) is reflected back to the
measuring device (dashed red arrows in Figure \ref{fig:cartoon}) and
$(1-\Gamma_{f})$ is radiated by the feed (solid red arrows in Figure
\ref{fig:cartoon}) which illuminates the dish. While most of the incident signal is reflected back into space by the dish, the reflected signal from the dish vertex returns to
the feed. This incident signal is now
reflected back and forth in between the feed and the dish much like the sky
signal reflection discussed previously.  Hence, if $P_{r}$ is the power
incident back on the feed for the first time then the reflected power, $P_{refl}$,
back into the VNA would be:

\begin{equation}\label{eqn:series2}
P_{refl} =  P_{r}(1-\Gamma_{f})[1+ \Gamma_{f}\Gamma_{d} e^{i\phi}+ (\Gamma_{f}\Gamma_{d})^2e^{i2\phi}+ ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{in\phi}]
\end{equation}

@@

Recall that $P_{r}$ is the initial power that is incident back on the feed, which is just the feed radiated power reflected off the dish:

\begin{equation}
P_{r}= \Gamma_{d}(1-\Gamma_f)e^{i\phi} P_{tr}
\end{equation}

@@

\begin{eqnarray}
P_{ret} & = & \Gamma_{f}P_{tr} \nonumber\\ 
 & + &   \Gamma_{d}(1-\Gamma_f)e^{i\phi} P_{tr}(1-\Gamma_{f}) [1+ \Gamma_{f}\Gamma_{d} e^{i\phi}+  ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{in\phi}]\nonumber\\
 \end{eqnarray}

@@

  \begin{eqnarray}\label{eqn:ratio2}
 {P_{ret} \over P_{tr} } & = & \Gamma_{f}
  +  \Gamma_{d}(1-\Gamma_f)^{2} [e^{i\phi}+ \Gamma_{f}\Gamma_{d} e^{i2\phi}+  ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{i n\phi}]\nonumber\\
  & = & \Gamma_{f} + { (1-\Gamma_f)^{2}\over \Gamma_{f} } \displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}e^{i\phi}]^{n}
   \nonumber\\
\end{eqnarray}

@@

The VNA measures the magnitude and phase of the quantity ${P_{ret}\over P_{tr}}$
as a function of frequency as shown in Figure \ref{fig:freq}. In our measurement
set-up, the first reflection occurs at the feed $\Gamma_{f}$, so
$({P_{ret} \over P_{tr} }  - \Gamma_{f}) $ gives an estimate of the delay
spectrum of the sky signal. In delay domain, the relative signal strength at
zero delay represents the factor $\Gamma_{f}$ while the signal strength at any
other delay represents any delayed signal that enters the feed after being
reflected from the feed surroundings.
